\documentclass[../../main.tex]{subfiles}

\begin{document}

\subsection{3.6 Multivalued Dependencies}

\subsubsection*{Exercise 6.1}

we can pair the $B$-value from any tuple with the
value of the remaining attribute C from any other
tuple.

Thus the tuples $(a, b_{1}, c_{2})$, $(a, b_{1}, c_{3})$,
$(a, b_{2}, c_{1})$, $(a, b_{2}, c_{3})$, $(a, b_{3}, c_{1})$,
and $a, b_{3}, c_{2}$ are also in $R$.

\subsubsection*{Exercise 6.2}

a)

From the description, we can get the following FD.

\begin{align*}
  S & \to NB \\
  CS & \to CN \\
  CS & \to CB \\
  AS & \to AM
\end{align*}

Also, we can get the following MVD.

\begin{align*}
  S & \twoheadrightarrow NB \\
  S & \twoheadrightarrow AS \\
  S & \twoheadrightarrow am
\end{align*}

b)

\begin{itemize}
  \item $R_{1}(S, CS, A)$
  \item $R_{2}(S,N,B)$
  \item $R_{2}(CS,CN,B)$
  \item $R_{4}(AS, M)$
\end{itemize}

\subsubsection*{Exercise 6.3}

a)

Left side is not a key and holds more than one MVD
so it violates 4NF.

We could decompose $R$ into $R_{1}(A, B)$, $R_{2}(A, C)$
and $R_{3}(A, D)$.

b)

For $B \twoheadrightarrow CD$, left side is not a key. So it
violates 4NF.

We could decompose $R$ into $R_{1}(A, B)$, $R_{2}(B, C, D)$.

c)

For $B \twoheadrightarrow D$, left side is not a key. It violates
4NF.

We could decompose $R$ into $R_{1}(A, B, C)$, $R_{2}(B, D)$.

d)

We could easily calculate $\{A\}^{+} = {A, B, C, D, E}$. So
all the left sides are keys. so it is in 4NF.

\subsubsection*{Exercise 6.4}

We have five attributes $(name, street, city, title, year)$

\begin{itemize}
  \item City is not determined by other four attributes as there
        can be same street address with different city.
  \item Year is not determined as there can be different address
        of one star.
  \item Title is not determines as with two same movie, different
        address is present.
  \item Street is not determined as with two same title, street is different.
  \item Name is not determined as with two same year and same movie star have different address.
\end{itemize}

None of the five attributes is determined by other four.

\end{document}
