\documentclass[../../main.tex]{subfiles}

\begin{document}

\subsection{15.2 One-Pass Algorithms}

\subsubsection*{Exercise 2.1}

Need community help.

\subsubsection*{Exercise 2.2}

a)

This is not a blocking operator. The projection operation does not need
entire relation to produce the output.

b)

This is not a blocking operator. The distinct tuple is always in the
memory.

c)

This is a blocking operator. To group we need to examine every tuple.

d)

This is not a blocking operator. Because we could read each
block into the buffer once at a time.

e)

This is not a blocking operator. The operation does not require the entire
tuple structure to produce the output.

f)

This can be or can not be a blocking operator. If the computation starts
from $R$ to $S$ then each block of $R$ is read and the operation is not blocking.
If R is read into $M-1$ blocks then each block of $S$ is read and the operation
is blocking.

g)

This is not a blocking operator. This operation does not need all the tuples
to produce the output.

h)

This can be or can not be a blocking operator. This operation is the similar
to the operation in the set difference.

i)

This is not a blocking operator. This operation does not need all the tuples
to produce the output.

j)

This is not a blocking operator. It just need the matching tuple between
the relations to produce the output.

\subsubsection*{Exercise 2.3}

Both arguments are not clustered which means we need to read every tuple.

\begin{table}[H]
  \centering
  \begin{tabular}{@{}ccc@{}}
  \toprule
  Operators                      & Memory required  & Disk I/O required \\ \midrule
  $\sigma$, $\Pi$                &   1              &        T          \\
  $\gamma$, $\delta$             &   1              &        T          \\
  $\cap$, $\cup$, $-$,$\times$   &   $T(S) / T(B)$  &     T(S) + T(R)   \\ \bottomrule
  \end{tabular}
\end{table}

$R$ is clustered and $S$ is not clustered

\begin{table}[H]
  \centering
  \begin{tabular}{@{}ccc@{}}
  \toprule
  Operators                      & Memory required  & Disk I/O required \\ \midrule
  $\sigma$, $\Pi$                &   1              &        T          \\
  $\gamma$, $\delta$             &   T              &        T          \\
  $\cap$, $\cup$, $-$,$\times$   &   $T(S) / T(B)$  &     B(R) + T(S)   \\ \bottomrule
  \end{tabular}
\end{table}

$R$ is not clustered and $S$ is clustered

\begin{table}[H]
  \centering
  \begin{tabular}{@{}ccc@{}}
  \toprule
  Operators                      & Memory required  & Disk I/O required \\ \midrule
  $\sigma$, $\Pi$                &   1              &        T          \\
  $\gamma$, $\delta$             &   T              &        T          \\
  $\cap$, $\cup$, $-$,$\times$   &   $B(S)$         &     T(R) + B(S)   \\ \bottomrule
  \end{tabular}
\end{table}


\subsubsection*{Exercise 2.4}

Need community help.

\end{document}
