\documentclass[../../main.tex]{subfiles}

\begin{document}

\subsection{15.4 Two-Pass Algorithms Based on Sorting}

\subsubsection*{Exercise 4.1}

Need community help.

\subsubsection*{Exercise 4.2}

(a)

$$
3 * (B(R) + B(S)) = 3 * (10000 + 10000) = 60000
$$


(b)

$$
5 * (B(R) + B(S)) = 5 * (10000 + 10000) = 100000
$$

(c)

$$
3 * (B(R) + B(S)) = 3 * (10000 + 10000) = 60000
$$

\subsubsection*{Exercise 4.3}

By using the extra buffers for saving disk I/O, we can also increase the
overall performance of I/O. Sometimes I/O is the bottleneck for the is
against improvement of runtime performance. That's why, it has a big role
in this system. But there are also some types of buffering of disk I/O. They
are single buffering, double buffering, circular buffer, an so on. A system
transmits data of I/O to one buffer while operating system empties the
other in double buffering.

\subsubsection*{Exercise 4.4}

Total number of disk I/O: sort relation $R$ and $S$ + ($y$-values $*$ number of
I/O)

a)

$$
4 (B(R)+B(S)) + (250 + (3 * 500)) = 9500
$$

b)

$$
4 (B(R)+B(S)) + (5 * 300) = 7500
$$

c)

$$
4 (B(R)+B(S)) + (10 * 150) = 7500
$$

\subsubsection*{Exercise 4.5}

a)

$$
2 (B(R)+B(S)) + (2 * 1750) = 6500
$$

b)

$$
2 (B(R)+B(S)) + (5 * 500) = 5500
$$

c)

$$
4 (B(R)+B(S)) + (10 * 150) = 7500
$$

\subsubsection*{Exercise 4.6}

(a)

$$
M = \sqrt{B} = 100
$$

(b)

$$
M = \sqrt{B} = 100
$$

(c)

$$
M = \sqrt{B(S)B(R)} = 10000
$$

\subsubsection*{Exercise 4.7}

Need community help.

\subsubsection*{Exercise 4.8}

Need community help.

\subsubsection*{Exercise 4.9}

Since the merging operation is used for sorting the sequence hence the
total time complexity is $O(M\log(M))$ and the space complexity
is $\log(M)$. The concerned term is the space complexity
here as the I/O operations take place on the disk memory and lesser the
consumption of space lesser will be the I/O operations. That is why the
amount by which the disk I/O operations will be reduced is equal to
$\log(M)$. So if there were $M$ I/O operations were to take place, now only $M
- \log(M)$ I/O operations would take place.

\end{document}
